### 2018-07-22 express2018/contraction.tex
Fixed below example 3.6: "As bisimilarity .." #6
Fixed p.5 l.13: between [15] and "This" is missing a dot. #26 (also #5, I think)

Bisimilarity  contraction is coarser than 
 the \emph{expansion  relation} 
$\expa$ \cite{sangiorgi2015equations} %, arun1992efficiency}.
This is a
preorder widely used in proof techniques for bisimilarity and that 
intuitively refines bisimilarity by 
 formalising the idea of `efficiency' between processes.
Clause (1) is the same in the two
preorders. But in clause (2) expansion uses 
$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
 moreover with
contraction the final derivatives are simply required to be bisimilar.
An expansion 
$P \expa Q$
tells us  that $Q$ is always at least as efficient as $P$, whereas  the
 contraction $P \mcontrBIS Q$  just says that $Q$ has the  possibility of
being at least as efficient as $P$.

@@

As  bisimilarity  and expansion, contraction is preserved by all operators but sum.

>>>>

Bisimilarity  contraction is coarser than 
 the \emph{expansion relation} 
$\expa$ \cite{sangiorgi2015equations,arun1992efficiency}.
This is a
preorder widely used in proof techniques for bisimilarity and that 
intuitively refines bisimilarity by 
 formalising the idea of `efficiency' between processes.
Clause (1) is the same in the two
preorders. But in clause (2) expansion uses 
$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
 moreover with
contraction the final derivatives are simply required to be bisimilar.
An expansion 
$P \expa Q$
tells us  that $Q$ is always at least as efficient as $P$, whereas  the
 contraction $P \mcontrBIS Q$  just says that $Q$ has the  possibility of
being at least as efficient as $P$.

@@

\hl{Like (weak)} bisimilarity and expansion, contraction is preserved by all operators but sum.
